\textbf{Spatio-temporal distinct patterns in variations of \(PM_{10}\) and \(PM_{2.5}\) relative to the recent drivings of emission sources in Mongolia}

### 2024-11-15 submission/manuscript.Rmd
outline

---
title: "**Spatio-temporal distinct patterns in variations of $PM_{10}$ and $PM_{2.5}$ relative to the recent drivings of emission sources in Mongolia**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
csl: nature-communications.csl #Get themes at <https://github.com/citation-style-language/styles>
fontsize: 11pt
geometry: margin=1.0in
---

@@

Significance of PMs in the climate system

* PM consists of dust and aerosol, and emissions. 
* particulate matters has a significant effects on the climate system, altering the solar incidence, cloud formation, and precipitation. 
* concentrations of particulate matter is ephederemal, yet vary depending on whether the pollution cause is natural or industrial, local or transported, seasonal or non-seasonal, makes complex and challenging.

Moreover, emerging shifts in the PM emissions and their patterns alters continuously due to their dependencies on various drivings.

* It is well-informed that concentrations of air particulate matter solely depend on urbanization and economic situations to the area of the interest of the country. Globally, 7.3 billion people are directly exposed to unsafe average annual PM2.5 concentrations, and 80% of them living in low- and middle-income countries, where economies often rely heavily on polluting industries. A similar pattern of the significant disparities in air quality among income and racial/ethnic groups, as well as between urban and rural areas was reported in USA (Liu et al., 2021). Despite this disparity, meteorological effects such as dust storm, stagnant weather plays important role in the spatiotemporal variability of PM10 and PM2.5.

Similarly, Mongolia might turn into the not only coarse-dust source region but also fine-mixed coarse-dust region.

* Use of coal is increased 
* Urbanization 
* The monthly mean concentrations of PM10 (PM2.5) reached annual maximum in December and January due to winter synoptic governing conditions in Ulaanbaatar, capital city of Mongolia (Jugder). 
* Despite this, the spring dust storms creates another polluted season in UB. On spring, the dust storm from the Gobi Desert contribute significantly to increased aerosols in the atmosphere and ambient air pollution, leading to sporadic peaks in PM10 concentrations reaching as high as 64-234 $\mu g m^{-3}$ per day or exceeding 6000 $\mu g m^{-3}$ per hour (Jugder). 
* Siberian anticyclonic activity governed over Mongolia, which create a significant vulnerability to winter air pollution in the populated areas. 
* A such changes in PM10 and PM2.5 to stagnant weather conditions, and local or transported dust was also observed in other countries China (Wang), Korea (Kim) and Japan ().

* On downwind regions
* On national-level
Demonstrating temporal and spatial variations of air particulate matter has become important for understanding characteristics of particulate matter in the climate system, providing valuable information for well-established air quality measures, and illustrating the good trace data for health studies. Because particulate pollutants have a great impact on human health (Dockery and Pope,1994; Harrison and Yin, 2000; Hong et al., 2002), high atmospheric concentrations of these pollutants was a major concern particularly in urban areas, in the last 2-3 decades. Recent studies highlight that even low concentrations of these pollutants can lead to various health issues, and may associate with morbidity and mortality across the life span (Zigler et al., 2017). Children exposed to high levels of air pollution show increased rates of asthma, decreased lung function growth, and increased risk of early markers of cardiovascular disease (Bourdrel et al., 2017; Gauderman et al., 2015; Hehua et al., 2017). Short-term exposure with high level of PM10 resulted the chronic cardiovascular disease in Mongolia (Enkhjargal 2020). In addition to these health issues, (prenatal) neurodevelopmental impacts such as effects on intelligence, attention, autism, and mood, while aging populations experience accelerated cognitive decline when exposed to high levels of pollution is detected (Power et al., 2016). Long-term exposure to low levels of particulate matter, such as concentrations as low as 10 $\mu g m^{-3}$ (equilibrium to WHO Air Quality Guidelines), has been linked to increased lung cancer in the EU (Hvidtfeldt et al. 2021), with similar evidences reported in Canada (Bai et al., 2019), and significantly higher rates captured in China with concentrations up to 30 $\mu g m^{-3}$. Apparently, pollutants of particulate matters has effects to various health issues with the different thresholds and exposure durations. However, more in-depth and diversified research on air pollution and its health effects is essential, with the detailed information is necessary (Tan et al 2021) to have accuracy of assessing exposure to air pollution during developmentally relevant time periods, such as trimesters or months (Becerra et al., 2013; Gong et al., 2014; Kalkbrenner et al., 2014) or weeks (Chiu et al., 2016). Many research findings/Numerous research findings have advanced the field, and air quality indices is widely used for providing guidance, and public perception of air quality has been improved (Mirabelli et al., 2020).

@@

* The present study will contribute significantly to the understanding of air particulate matter patterns in Mongolia and providing comprehensive data insights for policymakers and public health sectors. 
* Our findings is useful not only for addressing national health impacts but also beneficial for understanding air particulate matter as ambient air pollution, and tackling atmospheric aerosol effects in the climate system, and revealing their transboundary effects to the downwind regions in South-east Asia.

@@

[@Schloss2009] dksl ss [@Munkh2017] **Figure 3. Geographic locations of study sites** is shown in the wind speed map and elevation maps.

@@

@@

**Figure 1. Geographic locations of study sites** is shown in the wind speed map and elevation maps.

**Table 1. A description of datasets obtained at the sites**

**Figure 2.** is shown in the wind speed map and elevation maps.

\cite{Schloss2009} \newpage

>>>>

---
title: "**Spatio-temporal distinct patterns in variations of $PM_{10}$ and $PM_{2.5}$
  relative to the recent drivings of emission sources in Mongolia**"
bibliography: references.bib
output:
  pdf_document:
    keep_tex: true
    includes:
      in_header: header.tex
  html_document:
    df_print: paged
csl: "nature-communications.csl"
fontsize: 11pt
geometry: margin=1.0in
editor_options:
  markdown:
    wrap: 72
---

@@

Mongolian dust is well-known by its term of coarse, \* color of brown,
\* its influence on downwind regions, \* and big role in global dust, \*
and its seasonality.

Because, it mainly consists of coarse fractions researchers neglect its
role in global climate into elaborating global dust-aerosol effects.
*However, recent change in the driving of the emissions of particulate
matters might cause fluctuations* its spatio-temporal variations and \*
characteristics and \* emerge a new pattern, eventually it may lead to
the role in the regional and global dust, so on climate system through
\* altering solar incidence, cloud formation, and precipitation or
warming \* the climate with the fraction of finer particulates.

Mongolia might turn into the not only coarse-dust source region but also
fine-mixed coarse-dust region.

-   Use of coal is increased

-   Urbanization

-   The monthly mean concentrations of PM10 (PM2.5) reached annual
    maximum in December and January due to winter synoptic governing
    conditions in Ulaanbaatar, capital city of Mongolia (Jugder).

-   Despite this, the spring dust storms creates another polluted season
    in UB. On spring, the dust storm from the Gobi Desert contribute
    significantly to increased aerosols in the atmosphere and ambient
    air pollution, leading to sporadic peaks in PM10 concentrations
    reaching as high as 64-234 $\mu g m^{-3}$ per day or exceeding 6000
    $\mu g m^{-3}$ per hour (Jugder).

-   Siberian anticyclonic activity governed over Mongolia, which create
    a significant vulnerability to winter air pollution in the populated
    areas.

-   A such changes in PM10 and PM2.5 to stagnant weather conditions, and
    local or transported dust was also observed in other countries China
    (Wang), Korea (Kim) and Japan ().

-   deposition

-   concentrations of particulate matter is ephederemal, yet vary
    depending on whether the pollution cause is natural or industrial,
    local or transported, seasonal or non-seasonal, makes complex and
    challenging.

@@

-   The present study will contribute significantly to the understanding
    of air particulate matter patterns in Mongolia and providing
    comprehensive data insights for policymakers and public health
    sectors.
-   Our findings is useful not only for addressing national health
    impacts but also beneficial for understanding air particulate matter
    as ambient air pollution, and tackling atmospheric aerosol effects
    in the climate system, and revealing their transboundary effects to
    the downwind regions in South-east Asia.

@@

\newpage
\subsection{Urban and rural distinct Spatio-temporal diverse variations of $PM_{10}$ and $PM_{2.5}$}

![Distinct concentrations of coarse and fine particulates among
sites](images/figure_3.png){width="300"}

1.  Compare the concentrations of PMs at UB is the 2. Significance level
    difference 3. Conclude

![Annual variations of \$PM\_{10}\$ and
\$PM\_{2.5}\$](images/figure_4.png){width="330"}

 1. Clear annual variations at UB and DZ from pm2.5 pollutions 2. at ZU,
and SS has a seasonally peaks episodic spring and late autumn from PM10

![Daily variations of $PM_{10}$ and $PM_{2.5}$ at UB and DZ
sites](images/figure_5.png){width="300"}

\newpage
\subsection{Meteorological influence on $PM_{10}$ and $PM_{2.5}$ variations}
\label{subsec2}

![Relationships between meteorological major factors and variations of
$PM_{10}$ and $PM_{2.5}$](images/figure_6.png){width="300"}

![Spatio-temporal distinct feature of variations of $PM_{10}$ and
$PM_{2.5}$ with PCA analysis](images/figure_7.png){width="200"}

![Patterns of meteorology and PMs at the 4
sites](images/figure_7b.png){width="200"}

\newpage
\subsection{Trends}

![Interannual and seasonal trends of $PM_{10}$ and $PM_{2.5}$
variations](images/figure_8.png){width="300"}

@@

In this study, we investigated the temporal variations of PM2.5 and PM10
concentrations at the 4 sites of rural and urban those located along the
the wind corridor. Three distinct variations has been detected.

\begin{enumerate}
    \item Air quality in urban sites is episodically dictated by dust events in spring or late autumn, yet seasonally governed by anthropogenic emissions in winter.
    \item Air quality in rural sites of SS and ZU is episodically dictated by dust events in spring or late autumn.
    \item Air quality in rural sites of SS and ZU is episodically dictated by dust events in spring or late autumn.
\end{enumerate}

A clear seasonal variations in the sites of UB and DZ is [Air quality is
governed by natural dust emission, and anthropogenic emissions] \* Due
to rapid increase in urban, and combustion of coal/oyutolgoi for heating
winter conditions results a highly increase in not only capital city but
also towns \* In a result, spring coarse dust, plus winter fine
pollutants [spring coarse dust is immediately transported and deposited
in the source area, whereas winter fine pollutants is permanently stayed
in the source area due to stagnant atmosphere govern over entire
country., perhaps float- ing in the near surface, deposits in the
surface] \* Alarms, the Mongolian dust in the spring, optical properties
will be shifted; this gives ... Gobi dust and sand storms has become
tuiren, from the shoroon shuurga. which clearly requires the attention.

-   On downwind regions
-   On national-level Demonstrating temporal and spatial variations of
    air particulate matter has become important for understanding
    characteristics of particulate matter in the climate system,
    providing valuable information for well-established air quality
    measures, and illustrating the good trace data for health studies.
    Because particulate pollutants have a great impact on human health
    (Dockery and Pope,1994; Harrison and Yin, 2000; Hong et al., 2002),
    high atmospheric concentrations of these pollutants was a major
    concern particularly in urban areas, in the last 2-3 decades. Recent
    studies highlight that even low concentrations of these pollutants
    can lead to various health issues, and may associate with morbidity
    and mortality across the life span (Zigler et al., 2017). Children
    exposed to high levels of air pollution show increased rates of
    asthma, decreased lung function growth, and increased risk of early
    markers of cardiovascular disease (Bourdrel et al., 2017; Gauderman
    et al., 2015; Hehua et al., 2017). Short-term exposure with high
    level of PM10 resulted the chronic cardiovascular disease in
    Mongolia (Enkhjargal 2020). In addition to these health issues,
    (prenatal) neurodevelopmental impacts such as effects on
    intelligence, attention, autism, and mood, while aging populations
    experience accelerated cognitive decline when exposed to high levels
    of pollution is detected (Power et al., 2016). Long-term exposure to
    low levels of particulate matter, such as concentrations as low as
    10 $\mu g m^{-3}$ (equilibrium to WHO Air Quality Guidelines), has
    been linked to increased lung cancer in the EU (Hvidtfeldt et al.
    2021), with similar evidences reported in Canada (Bai et al., 2019),
    and significantly higher rates captured in China with concentrations
    up to 30 $\mu g m^{-3}$. Apparently, pollutants of particulate
    matters has effects to various health issues with the different
    thresholds and exposure durations. However, more in-depth and
    diversified research on air pollution and its health effects is
    essential, with the detailed information is necessary (Tan et al
    2021) to have accuracy of assessing exposure to air pollution during
          developmentally relevant time periods, such as trimesters or
          months (Becerra et al., 2013; Gong et al., 2014; Kalkbrenner
          et al., 2014) or weeks (Chiu et al., 2016). Many research
          findings/Numerous research findings have advanced the field,
          and air quality indices is widely used for providing guidance,
          and public perception of air quality has been improved
          (Mirabelli et al., 2020).

@@

![Geographic locations of study
sites](images/figure_1.png){width="300"}]

![**Table 1**. A description of datasets obtained at the
sites](images/table_1.png){width="400"}

![Scheme 1. Data handling procedure](images/scheme_1.png){width="300"}

![Figure 2. Data gap filling](images/figure_2b.png){width="300"}

![Figure 2b. Data gap filling](images/figure_2c.png){width="300"}

### 2024-11-15 submission/manuscript.tex
outline

\usepackage{pdfpages}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={NAME OF THIS STUDY},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{\textbf{NAME OF THIS STUDY}}
\author{}
\date{\vspace{-2.5em}}

@@

\subsection{ff}\label{ff}

csl: mbio.csl \#Get themes at
\url{https://github.com/citation-style-language/styles}

@@

Munkh\^{}1, Joeseph P. Schmo\^{}2, Sally J. Rivers\^{}1, Patrick D.
Schloss\textsuperscript{1\(\dagger\)}

@@

@@

@@

@@

@@

Insert figure legends with the first sentence in bold, for example:

\textbf{Figure 1. Number of OTUs sampled among bacterial and archaeal
16S rRNA gene sequences for different OTU definitions and level of
sequencing effort.} Rarefaction curves for different OTU definitions of
Bacteria (A) and Archaea (B). Rarefaction curves for the coarse
environments in Table 1 for Bacteria (C) and Archaea (D).

>>>>

\usepackage{pdfpages}
\usepackage{bookmark}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={Spatio-temporal distinct patterns in variations of PM\_\{10\} and PM\_\{2.5\} relative to the recent drivings of emission sources in Mongolia},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

\title{\textbf{Spatio-temporal distinct patterns in variations of
\(PM_{10}\) and \(PM_{2.5}\) relative to the recent drivings of emission
sources in Mongolia}}
\author{}
\date{\vspace{-2.5em}}

@@

@@

Munkh\^{}1, Joeseph P. Schmo\^{}2, Sally J. Rivers\^{}1, Patrick D.
Schloss\textsuperscript{1}\(\dagger\)

@@

Storyline:

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  A new pattern is emerged
\item
  Air quality in urban sites is episodically dictated by dust events in
  spring or late autumn, yet seasonally governed by anthropogenic
  emissions in winter. {[}Air quality is governed by natural dust
  emission, and anthropogenic emissions{]}
\item
  With recent growing interest in urban life style, and combustion of
  coal/oyutolgoi for heating winter conditions results a highly increase
  in not only capital city but also towns
\item
  In a result, spring coarse dust, plus winter fine pollutants
\item
  spring coarse dust is immediately transported and deposited in the
  source area, whereas winter fine pollutants is permanently stayed in
  the source area due to stagnant atmosphere govern over entire
  country., perhaps floating in the near surface, deposits in the
  surface{]}
\item
  Alarms, the Mongolian dust in the spring, optical properties might be
  shifted; this gives \ldots{} Gobi dust and sand storms has become
  tuiren, from the shoroon shuurga. which clearly requires the
  attention.
\item
  r ratio shows \ldots{} emission source; dust might carry anthropogenic
  fine particulates as well. \newpage
\end{enumerate}

Mongolian dust is well-known by its term of coarse, * color of brown, *
its influence on downwind regions, * and big role in global dust, * and
its seasonality.

Because, it mainly consists of coarse fractions researchers neglect its
role in global climate into elaborating global dust-aerosol effects.
\emph{However, recent change in the driving of the emissions of
particulate matters might cause fluctuations} its spatio-temporal
variations and * characteristics and * emerge a new pattern, eventually
it may lead to the role in the regional and global dust, so on climate
system through * altering solar incidence, cloud formation, and
precipitation or warming * the climate with the fraction of finer
particulates.

Mongolia might turn into the not only coarse-dust source region but also
fine-mixed coarse-dust region.

\begin{itemize}
\item
  Use of coal is increased
\item
  Urbanization
\item
  The monthly mean concentrations of PM10 (PM2.5) reached annual maximum
  in December and January due to winter synoptic governing conditions in
  Ulaanbaatar, capital city of Mongolia (Jugder).
\item
  Despite this, the spring dust storms creates another polluted season
  in UB. On spring, the dust storm from the Gobi Desert contribute
  significantly to increased aerosols in the atmosphere and ambient air
  pollution, leading to sporadic peaks in PM10 concentrations reaching
  as high as 64-234 \(\mu g m^{-3}\) per day or exceeding 6000
  \(\mu g m^{-3}\) per hour (Jugder).
\item
  Siberian anticyclonic activity governed over Mongolia, which create a
  significant vulnerability to winter air pollution in the populated
  areas.
\item
  A such changes in PM10 and PM2.5 to stagnant weather conditions, and
  local or transported dust was also observed in other countries China
  (Wang), Korea (Kim) and Japan ().
\item
  deposition
\item
  concentrations of particulate matter is ephederemal, yet vary
  depending on whether the pollution cause is natural or industrial,
  local or transported, seasonal or non-seasonal, makes complex and
  challenging.
\end{itemize}

Therefore, we aimed to demonstrate the distinct temporal and spatial
variations of PM2.5 and PM10 across urban and rural Mongolia using
extensive data from 2008 to 2020.

\begin{itemize}
\tightlist
\item
  The present study will contribute significantly to the understanding
  of air particulate matter patterns in Mongolia and providing
  comprehensive data insights for policymakers and public health
  sectors.
\item
  Our findings is useful not only for addressing national health impacts
  but also beneficial for understanding air particulate matter as
  ambient air pollution, and tackling atmospheric aerosol effects in the
  climate system, and revealing their transboundary effects to the
  downwind regions in South-east Asia.
\end{itemize}

@@

\newpage
\subsection{Urban and rural distinct Spatio-temporal diverse variations of $PM_{10}$ and $PM_{2.5}$}

\begin{figure}
\centering
\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/figure_3.png}
\caption{Distinct concentrations of coarse and fine particulates among
sites}
\end{figure}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Compare the concentrations of PMs at UB is the 2. Significance level
  difference 3. Conclude
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=3.4375in,height=\textheight,keepaspectratio]{images/figure_4.png}
\caption{Annual variations of \$PM\_\{10\}\$ and \$PM\_\{2.5\}\$}
\end{figure}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Clear annual variations at UB and DZ from pm2.5 pollutions 2. at ZU,
  and SS has a seasonally peaks episodic spring and late autumn from
  PM10
\end{enumerate}

\begin{figure}
\centering
\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/figure_5.png}
\caption{Daily variations of \(PM_{10}\) and \(PM_{2.5}\) at UB and DZ
sites}
\end{figure}

\newpage
\subsection{Meteorological influence on $PM_{10}$ and $PM_{2.5}$ variations}
\label{subsec2}

\begin{figure}
\centering
\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/figure_6.png}
\caption{Relationships between meteorological major factors and
variations of \(PM_{10}\) and \(PM_{2.5}\)}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=2.08333in,height=\textheight,keepaspectratio]{images/figure_7.png}
\caption{Spatio-temporal distinct feature of variations of \(PM_{10}\)
and \(PM_{2.5}\) with PCA analysis}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=2.08333in,height=\textheight,keepaspectratio]{images/figure_7b.png}
\caption{Patterns of meteorology and PMs at the 4 sites}
\end{figure}

\newpage
\subsection{Trends}

\begin{figure}
\centering
\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/figure_8.png}
\caption{Interannual and seasonal trends of \(PM_{10}\) and \(PM_{2.5}\)
variations}
\end{figure}

@@

In this study, we investigated the temporal variations of PM2.5 and PM10
concentrations at the 4 sites of rural and urban those located along the
the wind corridor. Three distinct variations has been detected.

\begin{enumerate}
    \item Air quality in urban sites is episodically dictated by dust events in spring or late autumn, yet seasonally governed by anthropogenic emissions in winter.
    \item Air quality in rural sites of SS and ZU is episodically dictated by dust events in spring or late autumn.
    \item Air quality in rural sites of SS and ZU is episodically dictated by dust events in spring or late autumn.
\end{enumerate}

A clear seasonal variations in the sites of UB and DZ is {[}Air quality
is governed by natural dust emission, and anthropogenic emissions{]} *
Due to rapid increase in urban, and combustion of coal/oyutolgoi for
heating winter conditions results a highly increase in not only capital
city but also towns * In a result, spring coarse dust, plus winter fine
pollutants {[}spring coarse dust is immediately transported and
deposited in the source area, whereas winter fine pollutants is
permanently stayed in the source area due to stagnant atmosphere govern
over entire country., perhaps float- ing in the near surface, deposits
in the surface{]} * Alarms, the Mongolian dust in the spring, optical
properties will be shifted; this gives \ldots{} Gobi dust and sand
storms has become tuiren, from the shoroon shuurga. which clearly
requires the attention.

Following problems

\begin{itemize}
\tightlist
\item
  On downwind regions
\item
  On national-level Demonstrating temporal and spatial variations of air
  particulate matter has become important for understanding
  characteristics of particulate matter in the climate system, providing
  valuable information for well-established air quality measures, and
  illustrating the good trace data for health studies. Because
  particulate pollutants have a great impact on human health (Dockery
  and Pope,1994; Harrison and Yin, 2000; Hong et al., 2002), high
  atmospheric concentrations of these pollutants was a major concern
  particularly in urban areas, in the last 2-3 decades. Recent studies
  highlight that even low concentrations of these pollutants can lead to
  various health issues, and may associate with morbidity and mortality
  across the life span (Zigler et al., 2017). Children exposed to high
  levels of air pollution show increased rates of asthma, decreased lung
  function growth, and increased risk of early markers of cardiovascular
  disease (Bourdrel et al., 2017; Gauderman et al., 2015; Hehua et al.,
  2017). Short-term exposure with high level of PM10 resulted the
  chronic cardiovascular disease in Mongolia (Enkhjargal 2020). In
  addition to these health issues, (prenatal) neurodevelopmental impacts
  such as effects on intelligence, attention, autism, and mood, while
  aging populations experience accelerated cognitive decline when
  exposed to high levels of pollution is detected (Power et al., 2016).
  Long-term exposure to low levels of particulate matter, such as
  concentrations as low as 10 \(\mu g m^{-3}\) (equilibrium to WHO Air
  Quality Guidelines), has been linked to increased lung cancer in the
  EU (Hvidtfeldt et al. 2021), with similar evidences reported in Canada
  (Bai et al., 2019), and significantly higher rates captured in China
  with concentrations up to 30 \(\mu g m^{-3}\). Apparently, pollutants
  of particulate matters has effects to various health issues with the
  different thresholds and exposure durations. However, more in-depth
  and diversified research on air pollution and its health effects is
  essential, with the detailed information is necessary (Tan et al

  \begin{enumerate}
  \def\labelenumi{\arabic{enumi})}
  \setcounter{enumi}{2020}
  \tightlist
  \item
    to have accuracy of assessing exposure to air pollution during
    developmentally relevant time periods, such as trimesters or months
    (Becerra et al., 2013; Gong et al., 2014; Kalkbrenner et al., 2014)
    or weeks (Chiu et al., 2016). Many research findings/Numerous
    research findings have advanced the field, and air quality indices
    is widely used for providing guidance, and public perception of air
    quality has been improved (Mirabelli et al., 2020).
  \end{enumerate}
\end{itemize}

@@

\subsubsection{A description of study
sites}\label{a-description-of-study-sites}

According to the spatial magnitude of wind stress in Mongolia (Figure
1), the largest magnitude of wind speed is on the Gobi sites,
particularly those located in the southeast edge of the country.

\begin{itemize}
\tightlist
\item
  The impact of high winds on plant diversity varies across
  environmental gradients of precipitation and soil fertility (Milchunas
  et al., 1988).
\item
  In the desert steppe zone, species richness was lower in the drier
  years but did not vary with grazing pressure.
\item
  In the steppe zone, species richness varied significantly with grazing
  pressure but did not vary between years. Species richness is not
  impacted by grazing gradient in desert steppe, but it is in the steppe
  (Cheng et al., 2011).
\end{itemize}

In the last 2 decades, due to poverty and natural disasters there is
population immigration has taken place from the rural to urban,
especially to capital city of Mongolia. Due to tiny infrastructure to
provide the mega city with the dense population, it introduces the urban
pollution. Therefore, Ulaanbaatar air particulate matter mainly reflects
the coal burning, and partly, natural dust.

Consequently, the atmospheric environment and climate for Mongolian Gobi
has been impacted the most by frequent dust and and sand storm in the
spring.

Our study was carried out in Dalanzadgad (town center) (Tbl. 1; 43.57°N,
104.42°E), Sainshand (Tbl. 1; 44.87°N, 110.12°E) and Zamyn-Uud (Tbl. 1;
43.72°N, 111.90°E) in the Gobi Desert, and at Ulaanbaatar (Tbl.??.??°N,
104.42°E) (city center) located in the temperate Mongolian steppe of
Mongolia (Figure 2). Nomads and settlements of this sum have raised a
large number of livestock, and they rank at number 30 out of 329 sums
for the largest number of livestock raised per sum (Saizen et al.,
2010). In the last decade, the number of dust events associated with
wind erodibility increased by 30 \% in Bayan-Önjüül (Kurosaki et al.,
2011). This is an area where dust emissions activity has been monitored
on a long-term basis (Shinoda et al., 2010a) at a dust observation site
(DOS) adjacent to the study site (Fig. 1a). According to long-term
meteorological observations made at the monitoring station of the
Institute of Meteorology and Hydrology of Mongolia located near the
site, the prevailing wind direction is northwest. Mean annual
precipitation is 163 mm, and mean temperature is 0.1◦C for the period
1995 to 2005 (Shinoda et al., 2010b). Soil texture is dominated by sand
(98.1 \%, with only 1.3 \% clay and 0.6 \% silt; Table 1; Shinoda et
al., 2010a). Insert figure legends with the first sentence in bold, for
example:

@@

\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/figure_1.png}{]}

\begin{figure}
\centering
\includegraphics[width=4.16667in,height=\textheight,keepaspectratio]{images/table_1.png}
\caption{\textbf{Table 1}. A description of datasets obtained at the
sites}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/scheme_1.png}
\caption{Scheme 1. Data handling procedure}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/figure_2b.png}
\caption{Figure 2. Data gap filling}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=3.125in,height=\textheight,keepaspectratio]{images/figure_2c.png}
\caption{Figure 2b. Data gap filling}
\end{figure}
